Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-12-21 paper/aldebaran.tex
affiliation

\email{w.farr@bham.ac.uk, G.R.Davies@bham.ac.uk, b.pope@sydney.edu.au, txn016@student.bham.ac.uk, jimbarrett27@gmail.com}

@@

 The Villum Foundation, The Danish Council for Independent Research | Natural Sciences and 
 the Carlsberg Foundation are thanked for their support on building the SONG prototype on 
 Tenerife. 
 We thank Jens Jessen-Hansen, Rasmus Handberg and René Tronsgaard Rasmussen for their contribution
 to the development of the SONG data reduction pipeline and archive system.

>>>>

\email{w.farr@bham.ac.uk, G.R.Davies@bham.ac.uk, benjamin.pope@nyu.edu, txn016@student.bham.ac.uk, jimbarrett27@gmail.com}

@@

The Villum Foundation, The Danish Council for Independent Research~|~Natural Sciences and 
 the Carlsberg Foundation are thanked for their support on building the SONG prototype on 
 Tenerife. 
 We thank Jens Jessen-Hansen, Rasmus Handberg and René Tronsgaard Rasmussen for their contribution
 to the development of the SONG data reduction pipeline and archive system.
